### 2020-07-02 manuscript/manuscript.rmd
working on last section of main text

High-throughput sequencing allows investigators to readilly assemble matrices with hundreds or thousands of protein-coding genes (Extended Data Table 1). Studies of animal phylogeny have used a wide variety of different approaches to identifying and selecting genes for their matrices. As a result, the genes selected for analysis vary widely (Fig. 2, Extended Data Fig. 1). To explore this variation in gene sampling, we annotated each gene against SwissProt [@boeckmann:2003swiss] and Gene Ontology databases (Supplementary Table 1). These annotations show XXX. We identified the ribosomal protein and BUSCO genes [@waterhouse2017busco] in each data matrix (Extended Data Fig. 2). The animal BUSCO dataset contains 978 genes that tend to occur as a single copy used to assess the completeness of genome assemblies [@waterhouse2017busco]. All matrices have than 50% of the BUSCO genes, and several less than 20%. The fact that so many BUSCO genes are not in these matrices reflects that the gene selection criteria include many additional factors, such as high expression (since so many phylogenomic data are based on transcriptome data) and features of molecular evolution.

@@

Sampling of outgroup taxa (non-animals, in this case) is critical to phylogenetic rooting questions, since the node where the outgroup attaches to the ingroup tree is the root of the ingroup. There has therefore been extensive focus on improving outgroup sampling when testing phylogenetic hypotheses about rooting [@graham2002rooting]. To explore the issue in the context of rooting animals, several studies have progressively removed more distantly related outgroup taxa to test the effect of outgroup selection to ingroup topology [ @ryan2013genome; @pisani2015genomic]. Three progressively more inclusive clades have often been investigated: Choanomalia (animals plus most closely related Choanoflagellata), Holoza (Choanimalia plus more distantly related Holozoa) and Opisthokonta (Holozoa + Fungi).

@@

Our analyses above show that, while PhyloBayes CAT analyses of matrices with restricted outgroup sampling sometimes support Porifera-sister, IQ-TREE C60 analyses of the same matrices do not. There are several factors, including variations in models (C60 vs CAT), software (Phylobayes vs IQ-TREE), and implementation details (e.g., number of categories used to accommodate site heterogeneity) that could explain the new variation in results noted here. In published analyses, all these factors were confounded since all previous heterogeneous analyses used the CAT model in PhyloBayes. Here we seek to deconfound these factors to gain a finer-grained perspective on why results differ between analyses of the same matrices.

@@

A primary difference between site-heterogeneous models with C (like C60) and CAT are the number of substitutional categories that sites are assigned to. CAT models employ a Dirichlet process prior to infer number of substitutional categories across a phylogenetic data matrix, so the number of categories is variable. Models with C60 are set to 60 categories. Differences in analysis results could therefore be due to differences in the number of categories. We therefore first assessed the number of categories inferred from CAT model for each PhyloBayes analysis (Supplementary Table 4). (XX add mean number of ) The number of categories is considerable larger than 60 categories used in C60 models, with a mean of `r cat_categories$n_categories_poisson %>% mean() %>% round(1)` categories for Poisson+CAT analyses and `r cat_categories$n_categories_gtr %>% mean() %>% round(1)` categories for GTR+CAT analyses. This is a very large number of additional parameters that must be estimated from the data. When ModelFinder is used to select the number of categories in IG-TREE C models, it often selects a number far less than 60, suggesting that 60 is already too high according to BIC criteria (Supplementary Table 5). The fact that CAT is selecting ten fold more than 60 is consistent with the findings that CAT model often overestimate the true number of substitutional categories, especially for large data matrix from simulation analyses [@whelan2016let].

Once we established this large difference in category number, we sought to test its direct impact on animal root position. It is not possible to use more than 60 categories for C models in IQ-TREE, but the number of categories can be set *a priori* in Phylobayes. We therefore varied the number of categories in Phylobayes analyses (Fig. 4; Supplementary Table 6). We found that Poisson+nCAT60 analyses in PhyloBayes, like Poisson+C60 and WAG+C60 IQ-TREE analyses, provide strong support of Ctenophora-sister. This indicates that the difference in results between unconstrained CAT analyses in PhyloBayes and C60 analyses in IQ-TREE is not due to differences in the software, but due to the large difference, in excess of ten-fold, in the number of categories. When we sweep the number of categories, we can observe the transition from support for Ctenophora-sister to an unresolved root to Porifera-sister (Fig. 4), all within PhyloBayes. For example, for the Whelan2017_strict matrix this transition occurs between 60 -- 120 categories.

The GTR-CAT model often has a better model-fitting than Poisson-CAT model in published analyses, and it is also suggested a better performance than Poisson-CAT model (XX citations). Due to computational limitations of GTR models, we only ran GTR+CAT and GTR+nCAT60 models on matrices with Choanimalia sampling. We found that for both Whelan2017 and Philippe matrices shifted from Porifera-sister with Poisson-CAT model to Ctenophora-sister using GTR-CAT model. Moreover, we also found all results strongly supported the Ctenophora-sister with GTR-nCAT60 models.

@@

```
**Fig. 4.**  Sensitive analyses with representative data matrices analyzed by different number of substitutionary categories (nCAT) in PhyloBayes. Statistical support values (posterior probabilities) were obtained from three data matrcies using the site-heterogeneous Poisson-CAT model with different categories” (A) Phlippe2009_Choanozoa; (B) Philippe2009_Holozoa; (C) Whelan2017_full_Choanozoa; (D) Whelan2017_strict. Statistical support for Ctenophora-sister and Porifera-sister is indicated in orange and green, respectively. Support values are from the sensitive analyses are shown in Supplementary Table 6.

### Differences in phylogenetic signal between site- homogeneous and heterogeneous models

The distribution of phylogenetic signal has never been quantified in site-heterogeneous models and compared with site-homogeneous models. To further explore the effect of model selection and outgroup choices in animal origin, we next quantify the support of phylogenetic signal over two alternative hypotheses (T1: Ctenophora-sister (Fig. 1A); T2: Porifera-sister (Fig. 1B)) to three representative data matrices with different outgroup choice and models in both ML and BI framework (Extended Data Fig. 3). By calculating gene-wise log-likelihood scores between T1 and T2 for every gene ($\Delta$GLS) in each matrix, we found that Ctenophora-sister had the higher proportions of supporting genes in every analysis when using site-homogeneous models (LG or WAG in both IQ-TREE or PhyloBayes). Moreover, the outgroup choice has little impact on the distribution of the support of phylogenetic signal in sifte-homogeneous models. This finding is largely consistent with the results from past study that majority of phylogenetic signal is strongly favored in Ctenophora-sister hypothesis with site-homogeneous models in other data matrices [@shen2017contentious].

In contrast, the phylogenetic signal of site-heterogenous models changed dramatically compared to the site-homogenous models. Although Ctenophora-sister also had the higher proportions of supporting genes with C60 models, we found that the phylogenetic signal decreases in many genes using C60 models compared to site-homogeneous models, especially in matrices from Ryan2013_est that nearly 30% of genes changed from strong to week signal ($\Delta$|lnL|<2) (Extended Data Fig. 3; Supplementary Table 7). In contrast to the C60 models, the phylogenetic signal largely increased in Poisson-CAT models and more importantly, the outgroup choice has a major effect of the distribution of phylogenetic signal (Extended Data Fig. 3). We found that support for Ctenophora-sister largely decreases and Porifera-sister increases (~ 20% of sampled gene partitions) when exclusive of more distantly related outgroups with the Poisson-CAT models (Supplementary Table 7). These results here are further corroborated by our phylogenomic analyses in BI, which the support of Porifera-sister generally increases in Holozoa and Choanimalia matrices.

### Bias of data-recoding
There is growing interest in data-recoding and previous study [@feuda2017improved] hoped that data-recoding would reduce potential artifacts due to differences across species in amino acid frequencies. They report that posterior predictive (PP) analyses [@Bollback:2002to] indicate 6-state recoded analyses have better model adequacy than 20-state amino acid analyses, and "Porifera-sister was favored under all recoding strategies" in Whelan2015_D20 and Chang2015 data matrices. Here we focus on two aspects of Feuda *et al.* First, we found that many of their recoded analyses are actually unresolved (*i.e.*, without strong support for either Porifera-sister or Ctenophora-sister), and that the analyses with the best posterior predictive scores do not provide strong support for Porifera-sister (Extended Data Fig. 5). Second, we created four new random recoding schemes by shuffling the amino acids in the SR-6 scheme (see methods). When we applied each of these randomized codes to the Whelan matrix and analyzed them under the CAT-GTR+G model with PhyloBayes-MPI [@Lartillot:2013fg], we observed similar results as for the empirical SR-6 recoding. Like SR-6 recoding, random recoding increases support for Porifera-sister and improves the apparent adequacy of models to explain heterogeneity of states across taxa (PP taxon hetero mean and max, Extended Data Fig. 6). Thus, our analyses show the impact of recoding is largely due to discarding information, not accommodating variation in amino acid composition. These findings indicate that it is premature to accept Porifera-sister and reject Ctenophora-sister using data-recoding methods and recoding can be a problematic method for addressing compositional variation (see more detailed discussion in supplementary text).

## The current state of understanding and future direction
Resolving the root position of animal phylogeny that diverged ~ 650 million years ago has proven particularly difficult, even with large genome-scale phylogenomic data matrices. By synthesizing all past phylogenomic studies and perform new analyses to characterize difference between studies, we found the support of Porifera-sister can only be recovered by site-heterogeneous CAT models with the most closely related outgroups, and Ctenophora-sister in all other cases. Four factors contribute significantly to the previous incongruent results based on our analyses. First, the overlap of gene sampling and matrix is extremely low across different studies, leading to the difficult of directly compare the results across different studies. Second, the distribution of phylogenetic signal are largely varied between site-homogeneous and site-heterogeneous models. More importantly, site-heterogeneous models are also more sensitive to outgroup choice than site-homogeneous models, leading to different results even with the same data matrix with different outgroup choice. Third, we found that increase of number of substitutional categories coupled with a more simplistic model can change the root position of animal phylogeny. Last, we demonstrated that the support of Porifera-sister by data-recoding methods is potentially resulted by data reduction, not accommodation of compositional heterogeneity across species. Thus, the recovery of Porifera-sister needs more constraints than Ctenophora-sister.

@@

**Extended Data Fig. 3** The distribution of phylogenetic signal for two alternative topological hypotheses on the earliest-branching animal lineage with different models and outgroup choice in Philippe2009, Ryan2013 and Whelan2017_full matrices (with two outgroup sampling: Choanimalia and full matrices). The two alternative topological hypotheses are: Ctenophora-sister; T1 (Orange);Porifera-sister T2 (Green). Proportions of genes supporting each of two alternative hypotheses in the Philippe2009, Ryan2013_est and Whelan2017_full data matrices with differnet outgroups sampling and substitutional models. The GLS values for each gene in each data matrix are provided in Table S5. We considered a gene with an absolute value of log-likelihood difference of two as a gene with strong (|ΔlnL| > 2) or weak (|ΔlnL| < 2) phylogenetic signal.

@@

Feuda *et al.* [@Feuda:2017ew] tackled a difficult phylogenetic problem -- placing the root of the animal phylogeny [@King:2017ie]. In the past decade, some analyses have placed Ctenophora (comb jellies) and others Porifera (sponges) as the sister group to all other animals (Fig. Extended Data Fig. 3B). Feuda *et al.* [@Feuda:2017ew] present new phylogenetic analyses that they claim provide strong support for Porifera-sister. Their analyses consider datasets from studies by Chang *et al.* [@Chang:2015hl] and Whelan *et al.* [@Whelan:2015jj], both of which found support for Ctenophora-sister. Feuda *et al.* were concerned that these Ctenophora-sister results were artefacts of lineage-specific differences in amino acid frequencies. In an attempt to reduce these differences, they recoded the full set of twenty amino acids into six groups of amino acids. These groups have more frequent evolutionary changes within them than between them, based on empirical observations in large protein datasets [@Susko:2007ds]. The intent is to discard many lineage-specific changes, which are expected to fall within these groups. Rather than model compositional heterogeneity, as their title suggests, this approach discards heterogeneous information so that much simpler models with fewer states can be applied. They report that posterior predictive (PP) analyses [@Bollback:2002to] indicate 6-state recoded analyses have better model adequacy than 20-state amino acid analyses, and "Porifera-sister was favored under all recoding strategies". Here we focus on two aspects of Feuda *et al.* First, we point out that many of their recoded analyses are actually unresolved (*i.e.*, without strong support for either Porifera-sister or Ctenophora-sister), and that the analyses with the best posterior predictive scores do not provide strong support for Porifera-sister. Second, we present new analyses that show the impact of recoding is largely due to discarding information, not accommodating variation in amino acid composition. These findings indicate that it is premature to accept Porifera-sister and reject Ctenophora-sister. They also show that recoding can be a problematic method for addressing compositional variation.

>>>>

High-throughput sequencing allows investigators to readily assemble matrices with hundreds or thousands of protein-coding genes (Extended Data Table 1). Studies of animal phylogeny have used a wide variety of different approaches to identifying and selecting genes for their matrices. As a result, the genes selected for analysis vary widely (Fig. 2, Extended Data Fig. 1). To explore this variation in gene sampling, we annotated each gene against SwissProt [@boeckmann:2003swiss] and Gene Ontology databases (Supplementary Table 1). These annotations show XXX. We identified the ribosomal protein and BUSCO genes [@waterhouse2017busco] in each data matrix (Extended Data Fig. 2). The animal BUSCO dataset contains 978 genes that tend to occur as a single copy used to assess the completeness of genome assemblies [@waterhouse2017busco]. All matrices have than 50% of the BUSCO genes, and several less than 20%. The fact that so many BUSCO genes are not in these matrices reflects that the gene selection criteria include many additional factors, such as high expression (since so many phylogenomic data are based on transcriptome data) and features of molecular evolution.

@@

Sampling of outgroup taxa (non-animals, in this case) is critical to phylogenetic rooting questions, since the node where the outgroup attaches to the ingroup tree is the root of the ingroup. There has therefore been extensive focus on improving outgroup sampling when testing phylogenetic hypotheses about rooting [@graham2002rooting]. To explore the issue in the context of rooting animals, several studies have progressively removed more distantly related outgroup taxa to test the effect of outgroup selection to ingroup topology [ @ryan2013genome; @pisani2015genomic]. Three progressively more inclusive clades have often been investigated: Choanimalia (animals plus most closely related Choanoflagellatea), Holozoa (Choanimalia plus more distantly related Holozoa) and Opisthokonta (Holozoa + Fungi).

@@

There are several factors, including variations in models (C60 vs CAT), software (Phylobayes vs IQ-TREE), and implementation details (e.g., number of categories used to accommodate site heterogeneity) that could explain the new variation in results noted here among site heterogeneous models. In published analyses, all these factors were confounded since all previous heterogeneous analyses used the CAT model in PhyloBayes. Here we seek to deconfound these factors to gain a finer-grained perspective on why results differ between analyses of the same matrices.

@@

A primary difference between the C (like C60) and CAT site-heterogeneous models is the number of equilibrium frequency categories. CAT models employ a Dirichlet process prior to infer number of equilibrium frequency categories, so the number of categories is variable [@Lartillot:2004dq]. IQ-TREE implements C models [@si2008empirical] with a fixed number of categories, from C10 to C60. Differences in analysis results could therefore be due to differences in the number of categories. The number of categories inferred by CAT in PhyloBayes can be very high (Supplementary Table 4), with a mean here of `r cat_categories$n_categories_poisson %>% mean() %>% round(1)` categories for Poisson+CAT analyses and `r cat_categories$n_categories_gtr %>% mean() %>% round(1)` categories for GTR+CAT analyses. This requires is a very large number of additional parameters that must be estimated from the data. When ModelFinder is used to select the number of categories in IQ-TREE C models, it often selects a number far less than 60, suggesting that 60 is already too high according to BIC criteria (Supplementary Table 5). These findings are consistent with the concern that CAT models can overestimate the number of equilibrium frequency categories in simulated matrices [@whelan2016let].

Once we established this large difference in category number, we sought to test its direct impact on animal root position. It is not possible to use more than 60 categories for C models in IQ-TREE, but the number of categories can be set *a priori* in Phylobayes using nCAT. We therefore varied the number of categories in Phylobayes analyses (Fig. 4; Supplementary Table 6). We found that Poisson+nCAT60 analyses in PhyloBayes, like Poisson+C60 and WAG+C60 IQ-TREE analyses, provide strong support of Ctenophora-sister. This indicates that the difference in results between unconstrained CAT analyses in PhyloBayes and C60 analyses in IQ-TREE is not due to differences in the software, but due to the large difference, in excess of ten-fold, in the number of categories. When we sweep the number of categories in PhyloBayes, we observe the transition from support for Ctenophora-sister to an unresolved root to Porifera-sister (Fig. 4). For example, for the Whelan2017_strict matrix this transition occurs between 60 -- 120 categories.

Published studies have found that the GTR-CAT model often has a better fit than Poisson-CAT, and investigators have suggested that it is more appropriate than the Poisson-CAT model for this question (XX citations). Due to computational limitations of GTR models, we only ran GTR+CAT and GTR+nCAT60 models on matrices with Choanimalia sampling. We found that for both Whelan2017 and Philippe matrices shifted from Porifera-sister with Poisson-CAT model to Ctenophora-sister using GTR-CAT model. Moreover, we also found all results strongly supported the Ctenophora-sister with GTR-nCAT60 models.

@@

```
**Fig. 4.**  Sensitive analyses with representative data matrices analyzed by different number of equilibrium frequency categories (nCAT) in PhyloBayes. Statistical support values (posterior probabilities) were obtained from three data matricies using the site-heterogeneous Poisson-CAT model with different categories” (A) Phlippe2009_Choanozoa; (B) Philippe2009_Holozoa; (C) Whelan2017_full_Choanozoa; (D) Whelan2017_strict. Statistical support for Ctenophora-sister and Porifera-sister is indicated in orange and green, respectively. Support values are from the sensitive analyses are shown in Supplementary Table 6.

### Phylogenetic signal

To further explore the variation described above, we quantify the phylogenetic signal for Porifera-sister and Ctenophora-sister topologies across three representative data matrices when varying outgroup sampling and model (Extended Data Fig. 3). By calculating differences in log-likelihood scores for these topologies for every gene ($\Delta$GLS) in each matrix, we found that Ctenophora-sister had the higher proportions of supporting genes in every analysis when using site-homogeneous models (LG or WAG in both IQ-TREE or PhyloBayes). Moreover, the outgroup choice has little impact on the distribution of the support of phylogenetic signal in site-homogeneous models. This finding is largely consistent with the the previously observed distribution of support for Ctenophora-sister in other data matrices [@shen2017contentious].

Although a higher proportion of genes support Ctenophora-sister with site-heterogeneous C60 models, the phylogenetic signal decreases in many genes using C60 models compared to site-homogeneous models. In an extreme case, in matrices from Ryan2013_est nearly 30% of genes changed from strong to week Ctenophora-sister signal ($\Delta$|lnL|<2) (Extended Data Fig. 3; Supplementary Table 7). In contrast to the C60 models, the phylogenetic signal largely increased in Poisson-CAT models, and the outgroup choice has a major effect of the distribution of phylogenetic signal (Extended Data Fig. 3). We found that the number of genes that support Ctenophora-sister in analyses with CAT decreases from XXs in matrices with distant outgroups (Opisthokonta) to XXb when outgroups are restricted (Choanimalia, Supplementary Table 7).

The fact that support across genes for Ctenophora-sister is not sensitive to outgroup sampling under site homogenous models, but is sensitive under site heterogeneous models, indicates that XX.

### Other approaches to accommodating site heterogeneity

There are other approaches to addressing heterogeneity in equilibrium frequencies. For example, Feuda *et al.* [@Feuda:2017ew] emplyed recoding methods that recoded the full set of twenty amino acids into six groups of amino acids. These groups have more frequent evolutionary changes within them than between them, based on empirical observations in large protein datasets [@Susko:2007ds]. This approach could, like CAT and C models, address variation across sites, but it could also accommodate variation across lineages, and it was suggested that this approach favors Porifera-sister [@Feuda:2017ew]. Our own analyses (Supplementary text, Supplementary Fig. XX-XX) indicate, however that the impact of data recoding is is largely due to discarding information, not accommodating variation in amino acid composition. These findings indicate that it is premature to accept Porifera-sister and reject Ctenophora-sister using data-recoding methods and recoding can be a problematic method for addressing compositional variation.

## The current state of understanding and future direction
Resolving the placement of the root in the animal phylogeny has proven particularly difficult, even with large genome-scale phylogenomic data matrices. By synthesizing past phylogenomic studies and performing new analyses to characterize difference between studies, we confirm that support of Porifera-sister is only recovered by site-heterogeneous CAT models with sampling restricted to the most closely related outgroups. Four factors contribute significantly to the previous incongruent results based on our analyses. First, the overlap of gene sampling and matrix is extremely low across different studies, leading to the difficult of directly compare the results across different studies. Second, the distribution of phylogenetic signal are largely varied between site-homogeneous and site-heterogeneous models. More importantly, site-heterogeneous models are also more sensitive to outgroup choice than site-homogeneous models, leading to different results even with the same data matrix with different outgroup choice. Third, we found that increase of number of substitutional categories coupled with a more simplistic model can change the root position of animal phylogeny. Last, we demonstrated that the support of Porifera-sister by data-recoding methods is potentially resulted by data reduction, not accommodation of compositional heterogeneity across species. Thus, the recovery of Porifera-sister needs more constraints than Ctenophora-sister.

@@

**Extended Data Fig. 3** The distribution of phylogenetic signal for two alternative topological hypotheses on the earliest-branching animal lineage with different models and outgroup choice in Philippe2009, Ryan2013 and Whelan2017_full matrices (with two outgroup sampling: Choanimalia and full matrices). The two alternative topological hypotheses are: Ctenophora-sister; T1 (Orange);Porifera-sister T2 (Green). Proportions of genes supporting each of two alternative hypotheses in the Philippe2009, Ryan2013_est and Whelan2017_full data matrices with differnet outgroups sampling and substitutional models. The GLS values for each gene in each data matrix are provided in Table S5. We considered a gene with an absolute value of log-likelihood difference of two as a gene with strong (|ΔlnL| $\geq$ 2) or weak ( 0 < |ΔlnL| < 2) phylogenetic signal.

@@

There is growing interest in data-recoding and previous study [@feuda2017improved] hoped that data-recoding would reduce potential artifacts due to differences across species in amino acid frequencies. They report that posterior predictive (PP) analyses [@Bollback:2002to] indicate 6-state recoded analyses have better model adequacy than 20-state amino acid analyses, and "Porifera-sister was favored under all recoding strategies" in Whelan2015_D20 and Chang2015 data matrices. Here we focus on two aspects of Feuda *et al.* First, we found that many of their recoded analyses are actually unresolved (*i.e.*, without strong support for either Porifera-sister or Ctenophora-sister), and that the analyses with the best posterior predictive scores do not provide strong support for Porifera-sister (Extended Data Fig. 5). Second, we created four new random recoding schemes by shuffling the amino acids in the SR-6 scheme (see methods). When we applied each of these randomized codes to the Whelan matrix and analyzed them under the CAT-GTR+G model with PhyloBayes-MPI [@Lartillot:2013fg], we observed similar results as for the empirical SR-6 recoding. Like SR-6 recoding, random recoding increases support for Porifera-sister and improves the apparent adequacy of models to explain heterogeneity of states across taxa (PP taxon hetero mean and max, Extended Data Fig. 6).

Feuda *et al.* [@Feuda:2017ew] present new phylogenetic analyses that they claim provide strong support for Porifera-sister. Their analyses consider datasets from studies by Chang *et al.* [@Chang:2015hl] and Whelan *et al.* [@Whelan:2015jj], both of which found support for Ctenophora-sister. Feuda *et al.* were concerned that these Ctenophora-sister results were artefacts of lineage-specific differences in amino acid frequencies. In an attempt to reduce these differences, they recoded the full set of twenty amino acids into six groups of amino acids. These groups have more frequent evolutionary changes within them than between them, based on empirical observations in large protein datasets [@Susko:2007ds]. The intent is to discard many lineage-specific changes, which are expected to fall within these groups. Rather than model compositional heterogeneity, as their title suggests, this approach discards heterogeneous information so that much simpler models with fewer states can be applied. They report that posterior predictive (PP) analyses [@Bollback:2002to] indicate 6-state recoded analyses have better model adequacy than 20-state amino acid analyses, and "Porifera-sister was favored under all recoding strategies". Here we focus on two aspects of Feuda *et al.* First, we point out that many of their recoded analyses are actually unresolved (*i.e.*, without strong support for either Porifera-sister or Ctenophora-sister), and that the analyses with the best posterior predictive scores do not provide strong support for Porifera-sister. Second, we present new analyses that show the impact of recoding is largely due to discarding information, not accommodating variation in amino acid composition. These findings indicate that it is premature to accept Porifera-sister and reject Ctenophora-sister. They also show that recoding can be a problematic method for addressing compositional variation.
